sensi_an_rotations1. Start of sensitivity analysis for rotations.

### 2018-07-30 inst/documents/paper3/recent_resist_literature.Rmd
try different insecticides

#### Helps 2017 model of effect of high dose on resistance selection
*to do* look at this again. [@Helps2017] across a wide range of demographics etc.
"It is demonstrated that with high immigration resistance can be suppressed. This suppression how- ever, is rarely lost if the insecticide dose is reduced, and is absent altogether when individuals move from the treated population back into an untreated population. Reducing the dose of insecticide often resulted in slower development of resistance, except where the population combined a high influx of less resis- tant individuals into the treated population, a recessive resistance gene and a high efficacy, in which case reducing the dose of insecticide could result in faster selection for resistance.""

@@

>>>>

#### Helps 2017 model of effect of high dose on resistance selection in agriculture
*to do* look at this again. [@Helps2017] across a wide range of demographics etc.
for wos
"One management strategy that has long been advocated is the application of insecticides at the maximum permitted dose. This has been found, under some circumstances, to be able to prevent the resistance allele frequency from increasing. However this approach may, under different circumstances, lead to rapid selection for resistance to the insecticide."

"It is demonstrated that with high immigration resistance can be suppressed. This suppression however, is rarely lost if the insecticide dose is reduced, and is absent altogether when individuals move from the treated population back into an untreated population. Reducing the dose of insecticide often resulted in slower development of resistance, except where the population combined a high influx of less resis- tant individuals into the treated population, a recessive resistance gene and a high efficacy, in which case reducing the dose of insecticide could result in faster selection for resistance."

"Because insecticides can have adverse impacts on non-target organisms, regulators have to ensure that the maximum permitted dose on the product la- bel is also the minimum dose required to achieve effective control ( Anon, 2012 ). The process of determining that dose was described by Finney (1993) , as follows. In farm crops, there are many fac- tors that affect the level of control achieved with any given dose. Hence, if dose-response experiments are repeated across many sites and seasons, many different dose-response curves result. For practical purposes, the label recommended dose is usually set at the level which gives a high level of control in a high proportion of circumstances. Finney suggested 80–90% control in 80–90% of field experiments as a typical aim, although higher levels of control may be required for insect pests, for example, to prevent insect contam- ination in horticultural crops. There are two consequences of this process of determining the full label dose which are relevant to the analysis presented here. Firstly, the label dose will not be set at a level which gives 100% control, even of sensitive strains, since, as previously mentioned, this is not the aim of the maximum al- lowed dose specified on a product label. Hence, the modelling ap- proach presented assumes that it is not possible to drive resistant strains to extinction by insecticide treatment, within the range of doses permitted."

@@

#### Venter2017 Benchmarking insecticide resistance intensity bioassays
The operational effect of insecticides will depend on doses and the resistancve phenotypes of mosquitoes. Resistance intensity assays are a way of qauntifying this, here intensity assays are related to the resistance phenotypes of lab strains with characterised resistance mechanisms. 
probably Cite this in windows paper.

#### Mbida2018 nets collected from the field against kdr resistant mosquitoes
Shows that field collected nets kill all susceptible mosquitoes but low proportions of field collected mosquitoes. Genotyping the field collected mosquitoes exposed to the field collected nets (Table 4) showed that 7-35 % of the surviviors had the susceptible kdr allele and none of those killed had the resistance allele. This demonstrates that the nets are within the window of selection and will be selecting for kdr resistance.

#### Denholm1992
In an agricultural context points out that theory suggests that rotations and sequences should be equivalent.
"Despite theoretical misgivings regarding the benefit of alternations, the prevalence of this tactic in existing strategies on cotton and elsewhere demonstrates its intuitive appeal and relative ease of implementation." [@Denholm1992]

### 2018-07-30 inst/documents/rotations_notes.Rmd
try different insecticides

@@

~ ian interested in starting frequencies at 10e-4, can do that for the runs with different values per insecticide.
~ ian suggested talking to Simon if we need to run something for longer

1. check out these runs that have the mut-sel balance option enabled
df_res_all_rot_cost10000_mut_sel_bal.rda
2. check ability to do runs where insecticides differ

>>>>

*13/7/18*

ltst <- list(d=c(9,6),s=7)

This nearly does what I want but loses names of columns
paste0(ltst)
[1] "c(9, 6)" "7"

cool this does it :
lapply(ltst,toString)
$`d`
[1] "9, 6"
$s
[1] "7"

linputs2 <- lapply(linputs, toString)
df_in_out <- as.data.frame(c(linputs2, gens_rot=gens_rot, gens_seq=gens_seq))

Seems that with variable insecticides there are more runs where sequences are better (i.e. highly negative rot_minus_seq) ?

See :
df_res_all_rot1000-diffI-lowstart.rda

*17/7/18*
To be able to plot specific scenarios with different insecticides I need to get the strings that I saved above back into vectors.

strsplit seems it should do the job :

tst <- as.character(linputs$rr)
unlist(strsplit(tst,split=", ")) #note the space after the comma

*30/7/18*
continuing getting it to cope with multiple insecticides in sensi_an_rotaions

I'm trying to convert string representations of mutliple parameters (that were needed to save in an output file) back to vector versions so I can rerun function with them.

  linputs2 <- lapply(linputs, function(x) ifelse(grepl(",",x),
    as.numeric(unlist(strsplit(as.character(x),split=", "))),x))

Currently I just get the first value
> linputs$cost
[1] "0.0209911216050386, 0.00808626485522836, 0.0159290118375793"
> linputs2$cost
[1] 0.02099112

There was something a bit weird about the ifelse that meant just the first dimension was returned.
This now works :

  linputs <- lapply(linputs, function(x) if (!grepl(",",x)) x else
                                          as.numeric(unlist(strsplit(as.character(x),split=", "))))

Examples with different insecticides where sequences last much longer than rotations seem to be caused by one of the 3 insecticides lasting much longer in the sequence, in the rotation it gets to a stage where it is the only one remaining, and our changing algorithm doesn't allow switching back to it from itself.

@@

~ and run_id to outputs in sensi_an_rotations to make things easier in future, e.g. to identify runs with particular behaviour.

~ check on 1000 runs with lower startfreqs and differing insecticides 
~ is something weird going on favouring rotations more when insecticides differ ?
~ yes

~ ian interested in starting frequencies at 10e-4, can do that for the runs with different values per insecticide.
~ we won't run sensitivity analysis on those runs, but just to check that rotations and sequence runs still similar
~ ian suggested talking to Simon if we need to run something for longer

1. check out these runs that have the mut-sel balance option enabled
df_res_all_rot_cost10000_mut_sel_bal.rda
done 2. check ability to do runs where insecticides differ
